\documentclass[12pt]{article}

\begin{document}

\section{Data Model}

Source genomes are genome assemblies with from which annotations are mapped to
target genome assemblies.  A genome maybe both a source and target genome,
although not all target genomes will annotations making them suitable to be
source genomes.

For a given TransMap release consists of a fixed set of source genomes.  New
target genomes maybe added to a given release, however source genomes and
already mapped target genomes are not changed until a new release.  Not all source
genomes maybe available in the public genome browser.

\subsection{Source annotations}

The following source genome annotations sets maybe are if available:
\begin{itemize}
\item GENBANK mRNAs from UCSC BLAT alignment track
\item GENBANK splice ESTs from UCSC BLAT alignment track
\item RefSeq RNA alignments
\item Ensembl full gene predictions (not projection), including GENCODE
\end{itemize}


** The following data is create for each annotation set:
\begin{itemize}
\item PSL alignments of transcripts, with all qNames prefixed with source database and made unique.
  These can be actual
  alignments or artificial alignments generated from genome annotations. PSLs
  are stored in big PSL format.
\item Transcript sequences, either transcripts for alignments or predicted transcripts
  from genome sequences.  In FASTA format, indexed by samtools.
\item Metadata for transcript, these are not obtained for ESTs.  The following values in a TSV fike:
  \begin{itemize}
  \item transcript id in the form srcDb:transcript
  \item CDS, in GenBank format
  \item gene name
  \item gene id
  \item gene type
  \item transcript type
  \end{itemize}
\end{itemize}

\end{document}
