% http://www.sanger.ac.uk/Software/analysis/projector/


The TransMap process produces cross-species mRNA alignments by combining the
results of two alignment methods that are optimized for different tasks.
Alignments of cDNA sequences to their cognate genome are done using
BLAT\cite{}. BLAT is designed to align transcripts of at least 95\% identity
to DNA sequences, producing intron-spanning alignments of the full cDNA.
TransMap projects the cDNA to genome alignments through BLASTZ\cite{}
cross-species genomic alignments to a target species genome.  BLASTZ is a
highly-sensitive aligner, optimized for aligning diverged, orthologous
genomic sequences.

For this analysis, BLAT alignments of mouse RefSeq\cite{} mRNAs to their cognate
genome were obtained from the UCSC Genome Browser Database\cite{}.  These
alignments, along with the coding sequence annotations associated with the
mRNAs, provide annotations of gene structure in the genome.  BLASTZ chained
alignments of source genome (mouse) to the target genome (human or dog) are
used to project the mouse mRNA alignments to the target genome.  UCSC
alignment nets\cite{} are used to select syntenic alignments chains for use in
the mappings.  This filter step removes paralogous alignments, with the
exception of those causes by tandem duplication.

The TransMap cDNA alignments will show the results of evolutionary change in
the genes and hence will not be realistic gene models for the target organism.
A set of heuristic corrections are applied to attempt to compensated for
insertions, deletions, and the movement of splice sites and start and stop
codons.  This results in a prediction of an orthologous gene in the targer
species.  The prediction is then evaluated to determine if it forms a valid
gene model.  While there is some risk of the evolutionary corrections masking
a change resulting in a pseudogene, the comparison with the out-group TransMap
gene predictions makes it unlikely that a false-positive human-specific 
pseudogene will be predicted.




This algorithm, known as TransMap and illustrated in Figure 1,
results in predictions of orthologous gene structures in the target organism.



.  BLAT

 from RefSeq to the
    mouser genome were obtained from the UCSC Genome Browser Database . 

Since the alignments 
optimized for different alignment problems.
BLAT alignments




- mRNA BLAT alignments to mouse
- blastz alignment chain selection
- mapping of alignment and CDS


- evolutionary correction and scoring

